---
title: "P8105 Intro to Linear Regression"
author: "Linh Tran"
date: "3/1/2021"
output: 
   html_document: 
      toc: true
      toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

```

# Introduction to Linear Models

## Model fitting

Load and clean Airbnb dataset

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

Fit a model with price as an outcome that may depend on rating and borough

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

**Be careful with factors**: Factor level is treated as the reference. Changing refefence categories won't change fit, or statistical significance, but can affect ease of interpretation.

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type))

fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

## Tidying output

Some common functions for interacting with `lm` fits

```{r}
summary(fit)
summary(fit)$coef
coef(fit)
#fitted.values(fit)
```

### `broom` package for obtaining quick summary of the model and clean up the coefficient table (produce dataframes)

```{r}
fit %>%
  broom::glance()
```


```{r}
fit %>% 
  broom::tidy()
```

```{r}
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^borough", "Borough")) %>% 
  knitr::kable(digits = 3)
```


## Diagnostics

`modelr` package can be used to add residuals and fitted values to a dataframe

```{r}
modelr::add_residuals(nyc_airbnb, fit)
```

```{r}
modelr::add_predictions(nyc_airbnb, fit)
```

Like many things in the tidyverse, the first argument is a dataframe. That makes it easy to included steps adding residuals or predictions in pipeline of commands to conduct inspections and perform diagnostics.

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) + geom_violin()
```

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()

# large outliers in price, skewed residual distribution. Can transform the price variable (e.g. log transformation, or fitting a model that is robust to outliers)
```


## Hypothesis Testing

Testing nested models using `anova` function, summarized using `broom::tidy`

```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
  
```

**Only use for nested models**

## Nesting data fitting models to datasets nested within variables. (Different from fitting nested models)

Use `nest` to create a list column containing datasets and fit separate models to each.\

E.g., we might think that star ratings and room type affects price differently in each borough. One way to allow this kind of effect modification is through interaction term

```{r}
nyc_airbnb %>% 
  lm(price ~ stars * borough + room_type * borough, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


Alternatively, we can nest within boroughs and fit borough-specific models associating price with rating and room type:

```{r}
nest_lm_res = 
  nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results)


nest_lm_res %>% 
  select(borough, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  pivot_wider(
    names_from = term, values_from = estimate) %>% 
  knitr::kable(digits = 3)

```

## Example: assessment of neighborhood effects in Manhattan

```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(borough == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results)
```

Neighborhood-specific estimates for the coefficients related to room type

```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

## Code to fix a mixed model with neighborhood-level random intercepts and slopes for room type

```{r}
manhattan_airbnb %>% 
  lme4::lmer(price ~ stars + room_type + (1 + room_type | neighborhood), data = .) %>% 
  broom.mixed::tidy()
```


## Binary outcomes - Logistic regression



